Global Reach or Out of Reach

### 2019-05-10 Paper_markdown.Rmd
Working on latex error

---
title: "Global Reach or Out of Reach"
author: "Addison Huygens"
date: "May 10, 2019"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: no
    latex_engine: pdflatex
    template: svm-latex-ms2.tex.url
  word_document: default
citecolor: black
biblio-style: apsr
endnote: no
fontsize: 12pt
---

options(tinytex.verbose = TRUE)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(plyr)
library(tidyverse)
library(DataCombine)
library(haven)
library(dotwhisker)
library(data.table)
library(mlogit)
library(ggplot2)
library(margins)
library(nnet)
library(reshape2)

```
#Packages

```{r, include=FALSE, cache=TRUE}
options(tinytex.verbose = TRUE)
#Data generation process 
#Prepping datasets for merging.

@@

```{r, include=FALSE, cache=TRUE}
options(tinytex.verbose = TRUE)
#Merging datasets

@@

```{r, include=FALSE, cache=TRUE}
options(tinytex.verbose = TRUE)
#Variable Generation

@@

#Creating variable measuring relative capabilities
Master3 <- filter(Master3, cinca != -9, cincb != -9)
Master3 <- Master3 %>%
    mutate(Relative_Cap = cinca/cincb)
head(Master3$Relative_Cap, 1000)

@@

Master3 <- Master3 %>%
  rename(
    Contiguous = contig,
  )

@@

```{r, include=FALSE, cache=TRUE}
options(tinytex.verbose = TRUE)
#Statistical Tests

#Bivariate Logits
MID_BI_Log <- glm(Mid ~ US_Naval_Cap, data = Master4, family=binomial)
summary(MID_BI_Log)
dwplot(MID_BI_Log)

Force_BI_Log <- glm(Use_Force ~ US_Naval_Cap, data = Master4, family=binomial)
summary(Force_BI_Log)
dwplot(Force_BI_Log)

#Full Models
  #Logistic regression
MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally, data = Master4, family=binomial)
summary(MID_Full_Log)

dwplot(MID_Full_Log, show_intercept=TRUE, model_name = "Logistic Model", vline=geom_vline(xintercept=0), dot_args = list(size=3))
exp(coef(MID_Full_Log))

margins(MID_Full_Log)
margins(MID_Full_Log, at = list(US_Naval_Cap = 0:1))
cplot(MID_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")

Force_Full_Log2 <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master4, family=binomial)
summary(Force_Full_Log2)
dwplot(Force_Full_Log2, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
exp(coef(Force_Full_Log2))
test1 <- data.frame(exp(coef(Force_Full_Log2)))
ggplot(exp(coef(Force_Full_Log2)))

margins(Force_Full_Log2)
cplot(Force_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of (violent)MID given US naval capabilities")

MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War, data = Master4, family=binomial)
summary(MID_Full_Log)
dwplot(MID_Full_Log)

Force_Full_Log <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
summary(Force_Full_Log)
dwplot(Force_Full_Log)

  #Mlogit model
Hostility_Mlog <- mlogit(Hostility ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Mlogit2, refleve=0)

summary(Hostility_Mlog)
dwplot(Hostility_Mlog)

Master5 <- Master4
Mlogit2 <- mlogit.data(Master5, varrying=7:14, choice="Hostility", shape="wide") 
Mlogittest <- mlogit()

Master6 <- Master5
Master6$Hostility <- relevel(Master6$Hostility, ref = "0")
test <- multinom(Hostility ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master6)
summary(test)
z <- summary(test)$coefficients/summary(test)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) *2

exp(coef(test))
head(pp <- fitted(test))
test2 <- data.frame(Hostility = c("0", "1", "2", "3", "4"), US_Naval_Cap = mean(Master6$US_Naval_Cap), Relative_Cap = mean(Master6$Relative_Cap), Joint_Dem = mean(Master6$Joint_Dem), Major = mean(Master6$Major), Same_Region = mean(Master6$Same_Region), Contiguous = mean(Master6$Contiguous), Post_Cold_War = mean(Master6$Post_Cold_War), Lag_Mid = mean(Master6$Lag_Mid))
predict(test, Master6 = test2, "probs")

@@

This is a test

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex.url
title: "Global Reach or Out of Reach"
author: 
- name: Addison Huygens
  affiliation: University of Iowa
abstract: "Here's where you write 100 to 250 words, depending on the journal, that describe your objective, methods, results, and conclusion."
keywords: "Naval power hegemony"
date: "May 10, 2019"
fontsize: 12pt
spacing: single
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "bib$"))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
---

\begin{document}

\begin{titlepage}

test

\end{titlepage}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(tidyverse)
library(DataCombine)
library(haven)
library(dotwhisker)
library(data.table)
library(mlogit)
library(ggplot2)
library(margins)
library(nnet)
library(reshape2)

```{r, include=FALSE, cache=TRUE}

#Data generation process 
#Prepping datasets for merging.

@@

```{r, include=FALSE, cache=TRUE}

#Merging datasets

@@

```{r, include=FALSE, cache=TRUE}
#Variable Generation

@@

#Creating variable measuring relative capabilities
Master3 <- filter(Master3, cinca != -9, cincb != -9)
Master3 <- Master3 %>%
    mutate(Relative_Cap = (cinca/cincb)/100000)
head(Master3$Relative_Cap, 1000)

@@

Master3 <- Master3 %>%
  rename(
    Contiguous = contig
  )

@@

```{r, include=FALSE, cache=TRUE}

#Statistical Tests

#Bivariate Logits
MID_BI_Log <- glm(Mid ~ US_Naval_Cap, data = Master4, family=binomial)
summary(MID_BI_Log)
ODDS_BI_MID <- exp(coef(MID_BI_Log))
dwplot(MID_BI_Log)

Force_BI_Log <- glm(Use_Force ~ US_Naval_Cap, data = Master4, family=binomial)
summary(Force_BI_Log)
ODDS_BI_FORCE <- exp(coef(Force_BI_Log))
dwplot(Force_BI_Log)

@@

\end{document}
